---
title: "Recognition of Activities of Daily Living Using a Wrist-Worn Accelerometer"
author: "Zach Quicksall (zsq2), Doyeon Kim (dkim1720), Nick Favale (favale2), Wenzheng Hu (whu14)"
date: "4/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset Description

The Data set for ADL Recognition with Wrist-worn Accelerometer’ is a public collection of labelled accelerometer data recordings to be used for the creation and validation of acceleration models of simple ADL. The Data set is composed of the recordings of 14 simple ADL (brush_teeth, climb_stairs, comb_hair, descend_stairs, drink_glass, eat_meat, eat_soup, getup_bed, liedown_bed, pour_water, sitdown_chair, standup_chair, use_telephone, walk) performed by a total of 16 volunteers. The data are collected by a single tri-axial accelerometer attached to the right-wrist of the volunteer.

## Dataset Background Information

[data location - UIC Machine Learning  Repository](https://archive.ics.uci.edu/ml/datasets/Dataset+for+ADL+Recognition+with+Wrist-worn+Accelerometer)

## Statistical Learning Task

Classification

## Data Structure

```{r, echo = FALSE}
phone = read.table("HMP_Dataset/Use_telephone/Accelerometer-2011-05-31-16-31-11-use_telephone-f1.txt", sep = " ")

head(phone)
```

```{r, echo = FALSE}
plot(phone$V1, type = "l", col = "dodgerblue", ylab = "Acceleration", main = "Using Phone")
lines(phone$V2, col = "darkorange")
lines(phone$V3, col = "darkgreen")
legend("bottom", xjust = 0.5, legend = c("X-Axis", "Y-Axis", "Z-Axis"), 
       inset = 0.05,  title = "Acceleration Direction",
       col = c("dodgerblue", "darkorange", "darkgreen"), lwd = 1)
```

## Data Modeling

We will use classification to predict the type of physical activity (brushing teeth, eating meat, pouring water, etc.) based on acceleration measurements provided by the data set. A substantial amount of data pre-processing will be necessary in order to model the data. The steps to perform this pre-processing are as follow:

For each observation, we have tri-axial accelerometer (x, y, z) measurements at 50 Hz. In order to make features, we will use two methods:

1. Vector quantize: We will cut the data in each observation to small segments with equal length. We will then use clustering technique to clusterize all segments we get from different observations and actions into k clusters. For each observation, we will then count how many of its segments belong to each cluster. As a result, for each observation, we have k features which indicate how many of its segments belong to each cluster k_i.

2. An alternative approach is to filter and segment each activity signal into smaller pieces. These sections will then be converted to feature vectors and paired with the activity in question. Models will be trained on these data to predict activity type.
